Sample-efficient Reinforcement Learning with Latent Representations

### 2024-01-28 paper/main.tex
started adding basic layout

@@

In humanoid-run and dog walk compare
\begin{itemize}
    \item Show that resetting is beneficial
    \begin{itemize}
        \item But picking when to reset varies across environments
    \end{itemize}
    \item DDPG
    \item DDPG reset every X param updates
    \item DDPG-AE
    \item DDPG-AE reset every X param updates
    \item DDPG-AE auto-resets
    \item DDPG-TAE
    \item DDPG-TAE reset every X param updates
    \item DDPG-TAE auto-resets
\end{itemize}

@@

\begin{itemize}
    \item Partial vs full resets vs $50\%$ resets etc
    \item Interleaved training vs representation first
    \begin{itemize}
        \item Show that representation first is better when resetting
        \item But interleaved better if not resetting
    \end{itemize}
    \item Normalized latent (SimNorm) vs unnormalized
\end{itemize}

\begin{itemize}
    \item Our method for auto-resetting handles sensors breaking during agents lifetime.
    \item Show this by transforming agents observations at some point during training.
\end{itemize}

\begin{itemize}
    \item When to reset actor/critic/encoder?
    \item How to pick UTD?
    \item How to pick learning rate?
\end{itemize}

@@

\textbf{Representation learning improves sample efficiency in RL}
\begin{theorem}
\label{thm:bigtheorem}
Given two MDPs $\left( \mathcal{S}_{1}, \mathcal{A}, P, r, \rho_{0}, \gamma \right)$ and $\left( \mathcal{S}_{2}, \mathcal{A}, P, r, \rho_{0}, \gamma \right)$
with $|\mathcal{S}_{1}| < |\mathcal{S}_{2}|$,
the optimal value function $V : \mathcal{S} \rightarrow \R$ in $\mathcal{S}_{1}$ can be learned with less environment samples than in $\mathcal{S}_{2}$.
\end{theorem}

\begin{proof}
Left as an exercise to the reader.
\end{proof}

\begin{corollary}
If $f:X\to Y$ is bijective,
the cardinality of $X$ is at least as large as that of $Y$.
\end{corollary}

\begin{assumption}
The state space $\mathcal{S}$ is discrete
\label{ass:discrete-state-space}
\end{assumption}

@@

\begin{itemize}
    \item Assume latent space contains all information from state space needed to predict values
    \item Show retraining better contains information from state space
    \begin{itemize}
        \item Train agent on $\mathcal{D}^{i}$ with old encoder $e_{\phi^{i-1}}$ and compare to new encoder $e_{\phi^{i}}$
    \end{itemize}
\end{itemize}

\section{Experiments}
\label{experiments}

SAC-AE is just SAC but using AE to get latent.
BDC use bisimulation metric so they can obtain bound on the suboptimality of a value
function trained on their representation.

\begin{itemize}
    \item Compare to SAC-AE
    \item Compare to TCRL
    \item Compare to SLAC
    \item Compare to SAC-BDC \citet{zhangLearningInvariantRepresentations2020}
    \item Compare to DeepMDP
    \item Compare to DHGP
\end{itemize}

\begin{itemize}
    \item Show we can use higher UTD?
    \item AE vs VAE vs VQ-VAE
    \item Full reset vs partial reset
    \begin{itemize}
        \item Reset last layer in MuJoCo
        \item Reset a percentage (\eg 50\%) on image observations
    \end{itemize}
    \item Compare to resetting every X parameter updates like in \citep{doroSampleEfficientReinforcementLearning2022}.
    \item How much training should we do after parameter reset?
    \item MuJoCo and Atari
\end{itemize}

>>>>

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=0.6\columnwidth]{./figs/diagram-self-predictive.png}}
\caption{Self-predictice loss}
\label{diagram-self-predictive}
\end{center}
\vskip -0.2in
\end{figure}

@@

\todo{Add algorithm}

\begin{align}
z_{t} &= e_{\theta} (s_{t}) \\
\hat{z}_{t+1} &= d_{\phi} (z_{t}, a_{t}) \\
q_{t} &= Q_{\psi} (z_{t}, a_{t}) \\
a_{t} &\sim \pi_{\eta} (z_{t}),
\end{align}

\textbf{Representation learning}
\begin{align}
  \mathcal{L}(\theta, \phi; \mathcal{D})
 % &= \E_{s_{t} \sim \mathcal{D}} \left[ \sum_{h=0}^{H-1} \| \hat{z}_{t+1} - z_{t+1} \|_{2}^{2} \right] \\
&= \E_{(s_{t}, a_{t}, s_{t+1}) \sim \mathcal{D}} \left[ \sum_{h=0}^{H-1} \| d_{\phi}(e_{\theta}(s_{t}), a_{t}) - e_{\bar{\theta}}(s_{t+1}) \|_{2}^{2} \right]
\end{align}

\textbf{Policy and value function learning}

\section{Experiments}
\label{sec:experiments}

\begin{itemize}
    \item Show normalised latent leads to higher sample efficiency. Show results for NTC-TD3/TC-TD3/TD3/SAC/TCRL/TD-MPC with UTD=1.
    \item Show normalised latent works with higher UTD. Compare NTC-TD3/TC-TD3/TCRL.
    \item Show task-agnostic representation is good for incremental task learning. Compare NTC-TD3/TCRL-ours/TCRL
\end{itemize}

@@

\begin{itemize}
  \item Show un-normalised isn't as good.
  \item Target encoder vs online encoder for mapping states to latents for TD3.
  \item Show cosine similarity slows training.
  \item Show adding reconstruction loss hurts performance.
\end{itemize}

@@

\textbf{Representation learning improves sample efficiency in RL}
% \begin{theorem}
% \label{thm:bigtheorem}
% Given two MDPs $\left( \mathcal{S}_{1}, \mathcal{A}, P, r, \rho_{0}, \gamma \right)$ and $\left( \mathcal{S}_{2}, \mathcal{A}, P, r, \rho_{0}, \gamma \right)$
% with $|\mathcal{S}_{1}| < |\mathcal{S}_{2}|$,
% the optimal value function $V : \mathcal{S} \rightarrow \R$ in $\mathcal{S}_{1}$ can be learned with less environment samples than in $\mathcal{S}_{2}$.
% \end{theorem}

% \begin{assumption}
% The state space $\mathcal{S}$ is discrete
% \label{ass:discrete-state-space}
% \end{assumption}

@@
